Region-network hierarchical sparsity priors for\\ high-dimensional inference in brain imaging

### 2016-01-24 paper/paper.tex
make it compile

% macros from michael's .tex
\DeclareMathOperator{\dist}{dist} % The distance.
\DeclareMathOperator{\argmin}{argmin}
\DeclareMathOperator{\argmax}{argmax}
\DeclareMathOperator{\Id}{Id}
\DeclareMathOperator{\abs}{abs}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}

@@

At the between-group level,...
$\Omega$ exerts $\ell_1$-like variable selection on
the (||\mathbf{w}_g||_2)_{g\inG} groups,
yielding a maximum of $g \in G$ to be zeroed out
\cite{jenatton2011structured}.
The important consequence is that also all descentes of such a zeroed
group $g \in G$ will be descarded.
Conversely,
if one group $g$ is selected,
then all the ancestral groups will also be selected.
Thus, statistical estimation will be improved by enticing
entire voxel sets to be selected or discarded as predictive, 
although one individual coefficient is computed for each voxel.

@@

(\eta_g)_{g \in G} are positive weights for the groups

@@

\begin{equation}
  P(y=k|x, W, b) = \frac{exp\{x^Tw^k + b_k\}}{\sum_{m=1}^cexp\{x^Tw^m + b_m\}}

  \argmin \frac{1}{2}||u-v||_2^2 + \lambda\Omega(\mathbf{w})

\end{equation}

\lambda > 0.

bias is omitted because \mathbf{X} and \mathbf{y}
are mean-centered and unit-variance scaled.

@@

\lambda > 0.

>>>>

% macros from michael's .tex
\DeclareMathOperator{\dist}{dist} % The distance.
%\DeclareMathOperator{\argmin}{argmin}
\DeclareMathOperator{\argmax}{argmax}
\DeclareMathOperator{\Id}{Id}
\DeclareMathOperator{\abs}{abs}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}

@@

At the between-group level,...
$\Omega$ exerts $\ell_1$-like variable selection on
the $(||\mathbf{w}_g||_2)_{g\in G}$ groups,
yielding a maximum of $g \in G$ to be zeroed out
\cite{jenatton2011structured}.
The important consequence is that also all descentes of such a zeroed
group $g \in G$ will be descarded.
Conversely,
if one group $g$ is selected,
then all the ancestral groups will also be selected.
Thus, statistical estimation will be improved by enticing
entire voxel sets to be selected or discarded as predictive, 
although one individual coefficient is computed for each voxel.

@@

$(\eta_g)_{g \in G}$ are positive weights for the groups

@@

\begin{equation}
  P(y=k|x, W, b) = \frac{exp\{x^Tw^k + b_k\}}{\sum_{m=1}^cexp\{x^Tw^m + b_m\}}
  \argmin \frac{1}{2}||u-v||_2^2 + \lambda\Omega(\mathbf{w})
\end{equation}

$\lambda > 0$

bias is omitted because $\mathbf{X} and \mathbf{y}$
are mean-centered and unit-variance scaled.

@@

$\lambda > 0$
